Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-09 text/src/article.tex
Delete additional files section

An example scaffold file written using the YAML syntax \cite{yaml}. The
scaffold file contains three entries. Each entry is delimited by a `-' on a new
line. The first entry is an example adding a simple sequence. The second entry
inserts an unresolved gap region into the scaffold. The final entry illustrates
a more complex examplea where the sequece is trimmed, reversed and has
additional sequence inserted \pb

\section*{Additional Files} %{{{1

  \subsection*{Additional file 1 --- Sample additional file title}
    Additional file descriptions text (including details of how to
    view the file, if it is in a non-standard format or the file extension).  This might
    refer to a multi-page table or a figure.

  \subsection*{Additional file 2 --- Sample additional file title}
    Additional file descriptions text.

>>>>

An example scaffold file written using the YAML syntax \cite{yaml}. The
scaffold file contains three entries. Each entry is delimited by a `-' on a new
line. The first entry is an example adding a simple sequence. The second entry
inserts an unresolved gap region into the scaffold. The final entry illustrates
a more complex examplea where the sequece is trimmed, reversed and has
additional sequence inserted. \pb
